Data_visualization

### 2018-09-07 Rmd/Data_visualization_common_names.Rmd
More changes in visualization file

```
\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
#load libraries

library(ggplot2)
library(colorspace)
library(gridExtra)

colours <- rainbow_hcl(4, start = 30, end = 300)
#load data

par(mfrow=c(2,1))
d<-read.csv("Data/Ovules.csv", sep=";")
d<- d[,-c(9,11)]
colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"
colnames(d)[9]<-"I. aquatica"
colnames(d)[10]<-"I. purpurea"

#Reorganise data
d <- stack(d)
#Naming columns
colnames(d)[1]<-"ovules"
colnames(d)[2]<-"species"

family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))

d[,"family"] <- family

#subset per family (solanaceae, brassicaceae, convolvulaceae)
solanaceae<-subset(d)[1:60,]
brassicaceae<-subset(d)[61:120,]

# OVULES SOLANACEAE
p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

# OVULES BRASSICACEAE
p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#all species
#formating d, to have just the spp of interest

p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

p <- read.csv("data/Pollen.csv", sep = ";")

#Deleting extra row (21)
p <-p[-21,]

#boxplot(p)
#Reorganize data for ggplot
p<-stack(p)
#colnames
colnames(p)[1]<-"pollen"
colnames(p)[2]<-"species"

all<-p
solanaceae<-subset(p)[1:100,]
brassicaceae<- subset(p)[101:180,]

#Solanaceae
p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Brassicaceae
p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#all
p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
tab <- read.csv("Data/tab.csv", sep="", header = T)

p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_fill_manual(values=colours)
p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")

@@

\newpage
###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES-
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

\newpage
###POLLEN PER ANTHER
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

```
\newpage

>>>>

@@

\newpage
###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

\newpage
###POLLEN PER ANTHER (N=20, I. aquatica N=10)
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())

@@

 ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="All species(-Eggplant)",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())

\newpage
###OVULES (N=15)
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}

d <- read.csv("Data/d.csv")

ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
  geom_boxplot(outlier.shape = NA)+labs(title="All species",x="", y = "Nº of ovules")+
  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
  scale_color_manual(values = cbPalette) + 
  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())

 d <- d[d$species !="Eggplant",]

 ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
  geom_boxplot(outlier.shape = NA)+labs(title="All species(-Eggplant)",x="", y = "Nº of ovules")+
  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
  scale_color_manual(values = cbPalette) + 
  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
library(dplyr)
library(ggplot2)

tab <- read.csv("Data/tab.csv", sep="", header = T)

ggplot(tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)
